The Morality of Arbitrage - Some Half-Baked Ideas

### 2017-06-23 Slides/apee-slides.Rmd
Updating slides for Mercatus.

> *But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who is only an economist is likely to become a nuisance if not a positive danger*.

-- Friedrich von Hayek

@@

@@

without leaving oneself open to a massive Dutch book. They are just two different examples of the very same thing!

>>>>

> But nobody can be a great economist who is only an economist - and I am even tempted to add that the economist who is only an economist is likely to become a nuisance if not a positive danger.
>
>>  -- Friedrich von Hayek

> The task of the modern educator is not to cut down jungles but to irrigate deserts. The right defense against false sentiments is to inculcate just sentiments. By starving the sensibility of our pupils we only make them easier prey to the propogandist when he comes. For famished nature will be avenged and a hard heart is no infallible protenction against a soft head.
>
>>  -- C.S. Lewis

@@

<br>
You might well ask why there is no ammendment that begins "congress shall make no law regarding the regulation of ..."

@@

without leaving oneself open to a massive Dutch book. They are merely two different examples of the very same thing!

### 2017-06-23 Slides/morality-slides.Rmd
Updating slides for Mercatus.

---
title: "The Morality of Arbitrage - Some Half-Baked Ideas"
author: "Tyler J. Brough"
date: "September 23, 2016"
output: ioslides_presentation
---

#

@@

-- Friedrich von Hayek

<div class="notes">
- Of course, all good ideas begin with Hayek!
</div>

>>>>

---
title: "The Morality of Arbitrage - Some Half-Baked Ideas"
author: "Tyler J. Brough"
date: "September 23, 2016"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

##

@@

> -- Friedrich von Hayek

<br>
<br>

> *The task of the modern educator is not to cut down jungles but to irriage deserts. The right defense against false sentiments is to inculcate just sentiments. By starving the sensibility of our pupils we only make them easier prey to the propagandist when he comes. For famished nature will be avenged and a hard heart is no infallible protection against a soft head.*

> -- C.S. Lewis

<div class="notes">
- Of course, all good ideas begin with Hayek!
- And Lewis!
</div>
